---
title: '**Comorbidity between mood and substance disorder - UNADJUSTED ESTIMATES**'
fontsize: 22pt
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
theme: united
font-family: Arial
---
<hr>
<br>

<style>
  
#TOC {
 position: fixed;
  left: 0;
  top: 0;
  width: 280px;
  height: 100%;
  overflow:auto;
}
body {
  max-width: 1200px;
  margin: auto;
  margin-left:150px;
  line-height: 20px;
}
h1.title {
    font-size: 28px;
}
h4 {
    font-size: 15px;
}
h3 {
    font-size: 16px;
}
h2 {
    font-size: 20px;
}
h1 {
    font-size: 24px;
}
.center {
    display: block;
    margin-left: auto;
    margin-right: auto;
    width: 28%;
}
.table {
    width: 40%;
}
</style>

\vspace{20mm}

<br>
<br>
**Author:** Carmen Lim \newline{}
<br>
<br>
**Report date:** 29 April 2021
<br>
<br>
<br>
<br>
<br>
<br>
\newpage
 
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, include = FALSE}
library(Matrix)
library(metafor)
library(ggplot2)
library(plotly)
library(here)
library(dplyr)
library(tinytex)
```

```{r readdata, echo = FALSE}
ma <- read.csv(here("data", "ma1.csv"))
ma1 <- ma[1:755,c("author_year","country","site", "temporality_type","pair","unadj_type","unadj_subtype","unadj_rate","unadj_lower",	"unadj_upper","unadj_pvalue", "a","b","c","d", "unadj_indicator","unadjusted_type", "adj_indicator", "M_EstimateType" )]
ma2 <- ma[1:755,c("author_year","country","site", "temporality_type","pair","adj_type","adj_subtype","adj_rate","adj_lower",	"adj_upper","adj_pvalue", "adj_indicator", "a","b","c","d","M_EstimateType"  )]
#ma$unadj_rate <- as.numeric(ma$unadj_rate)  

```

```{r function, echo = FALSE}
unadj_fn <- function(y2,z ){
dat2 <- escalc(measure="OR", ai=a, bi=b, ci=c, di=d, data=ma11)
dat2$yi <- replmiss(dat2$yi, log(dat2$unadj_rate))
dat2$zi <-sign(dat2$yi)*qnorm(dat2$unadj_pvalue/2, lower.tail = FALSE)
dat2$sei <- dat2$yi/dat2$zi
dat2$sei <- replmiss(dat2$sei, with(dat2, (log(unadj_upper) - log(unadj_lower))/(2*1.96)))
dat2$vi <- replmiss(dat2$vi, dat2$sei^2)
dat2$zi <- dat2$sei <-NULL
res2 <- rma(yi, vi, slab=paste(author_year,",",country),   data=dat2)
res2
print(predict(res2,transf=exp))
taf <- trimfill(res2)
forest(res2,atransf=exp, xlab="Unadjusted Odds Ratio" , cex = 0.7, xlim=c(-10, 7),   mlab="", at=log(c(0.01, 1, 5, 10, z)), psize=1.4,order=order(res2$yi))
par(font=2)
text(-10,   nrow(ma11)+1.5, cex = 0.7, "Study",  pos=4)
text(7,    nrow(ma11)+1.5, cex = 0.7, "Unadjusted Odds Ratio [95% CI]", pos=2)
text(-10, y2, pos=4,  cex = 0.7, bquote(paste("Heterogeneity (Q = ", .(formatC(res2$QE, digits=2, format="f")), ", df = ", .(res2$k - res2$p),", p = ", .(formatC(res2$QEp, digits=2, format="f")), "; ", I^2, " = ",
.(formatC(res2$I2, digits=1, format="f")), "%)")))
funnel(taf, legend=FALSE,cex=0.7, cex.lab= 0.8, cex.axis= 0.8 )
#funnel(taf, cex=0.7, cex.lab= 0.8, cex.axis= 0.8 )
#legend("topright", "Legend", cex = 0.7)
regtest(res2, model="rma") 
}


adj_fn <- function(y2,z ){
dat2 <- escalc(measure="OR", ai=a, bi=b, ci=c, di=d, data=ma22)
dat2$yi <- replmiss(dat2$yi, log(dat2$adj_rate))
dat2$zi <-sign(dat2$yi)*qnorm(dat2$adj_pvalue/2, lower.tail = FALSE)
dat2$sei <- dat2$yi/dat2$zi
dat2$sei <- replmiss(dat2$sei, with(dat2, (log(adj_upper) - log(adj_lower))/(2*1.96)))
dat2$vi <- replmiss(dat2$vi, dat2$sei^2)
dat2$zi <- dat2$sei <-NULL
res2 <- rma(yi, vi, slab=paste(author_year,",",country),   data=dat2)
print(predict(res2,transf=exp))
taf <- trimfill(res2)
forest(res2,atransf=exp, xlab="Adjusted Odds Ratio" ,cex=0.8, xlim=c(-10, 7), mlab="", at=log(c(0.01, 1,5,10, z)), psize=1.4,order=order(res2$yi))
par(font=2)
text(-10,  nrow(ma22)+1.5, cex = 0.7, "Study",  pos=4)
text(7,   nrow(ma22)+1.5, cex = 0.7, "Adjusted Odds Ratio [95% CI]", pos=2)
text(-10, y2, pos=4, cex=0.7, bquote(paste("Heterogeneity (Q = ",
                                      .(formatC(res2$QE, digits=2, format="f")), ", df = ", .(res2$k - res2$p),
                                      ", p = ", .(formatC(res2$QEp, digits=2, format="f")), "; ", I^2, " = ",
                                      .(formatC(res2$I2, digits=1, format="f")), "%)")))
funnel(taf, legend=FALSE,cex=0.7, cex.lab= 0.8, cex.axis= 0.8 )
regtest(res2, model="rma") 
#res2
}
```

# Temporally ordered Depression and alcohol abuse

###  Temporally estimates - UNADJUSTED
#```{r, echo = FALSE  }
ma11<- ma1 %>% filter(pair == "DEP-ALA" ) %>%
  filter(temporality_type == "TO") %>% 
  filter(unadj_indicator == "1") %>%
  filter(M_EstimateType == "odds ratios") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)

ma11<- ma1 %>% filter(pair == "DEP-ALD" ) %>%
  filter(temporality_type == "TO") %>% 
  filter(unadj_indicator == "1") %>%
  filter(M_EstimateType == "odds ratios") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)

ma22<- ma2 %>% filter(pair == "DEP-ALD" ) %>%
  filter(temporality_type == "TO") %>% 
  filter(adj_indicator == "1") %>%
  filter(M_EstimateType == "odds ratios") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)

ma22<- ma2 %>% filter(pair == "AUD-DEP" ) %>%
  filter(temporality_type == "TO") %>% 
  filter(adj_indicator == "1") %>%
  filter(M_EstimateType == "odds ratios") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
#```

#   Table 1. Broadly-defined mood disorder and substance use disorder
<br>
<br>
<br>
<br>


## 1. Mood disorder and Alcohol abuse

###  Lifetime estimates - UNADJUSTED
#```{r, echo = FALSE  }
#a1<- c("MOOD-ALA", "ALA-MOOD")
#ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
#  filter(unadj_indicator == "1") %>%
#  filter(unadjusted_type == "overall")
#unadj_fn(-1, 10)
#```

###  Lifetime estimates - ADJUSTED
#```{r, echo = FALSE  }
#a1<- c("MOOD-ALA", "ALA-MOOD")
#ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
#   filter(adj_indicator == "1") %>%
#  filter(adj_type == "overall")
#adj_fn(-1, 10)
#```

###  Period-prevalence estimates  - UNADJUSTED
```{r, echo = FALSE}
a1<- c("MOOD-ALA", "ALA-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10) 
```

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE}
a1<- c("MOOD-ALA", "ALA-MOOD")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```
<br>
<br>
<br>



## 2. Mood disorder and Alcohol dependence

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-ALD", "ALD-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Lifetime estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-ALD", "ALD-MOOD")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-ALD", "ALD-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

<br>
<br>
<br>

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-ALD", "ALD-MOOD")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 15)
```

<br>
<br>
<br>

## 3. Mood disorder and Alcohol Use Disorder

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-AUD", "AUD-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Lifetime estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-AUD", "AUD-MOOD")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-AUD", "AUD-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 30)
```

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-AUD", "AUD-MOOD")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```


<br>
<br>
<br>

## 4. Mood disorder and Drug Abuse

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-DRA", "DRA-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

<br>
<br>
<br>


## 5. Mood disorder and Drug dependence

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-DRD", "DRD-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
    filter(unadj_indicator == "1") %>%
    filter(unadjusted_type == "overall")
unadj_fn(-1, 50)
```

<br>
<br>
<br>

## 6. Mood disorder and Drug Use disorder

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-DUD", "DUD-MOOD")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

<br>
<br>
<br>


## 7. Mood disorder and SUD

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("MOOD-SUD", "SUD-MOOD")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 30)
```
<br>
<br>
<br>



#   Table 2. Broadly-defined dysthymia and substance use disorder
<br>
<br>
<br>
<br>

## 1. Dysthymia and Alcohol abuse

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-ALA", "ALA-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```
<br>
<br>
<br>

## 2. Dysthymia and Alcohol dependence

###  Lifetime estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-ALD", "ALD-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```
<br>
<br>
<br>

###  Lifetime estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-ALD", "ALD-DYS")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-ALD", "ALD-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

<br>
<br>
<br>

## 3. Dysthymia and Alcohol use disorder

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-AUD", "AUD-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

###  Lifetime estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-AUD", "AUD-DYS")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-AUD", "AUD-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-AUD", "AUD-DYS")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 30)
```


## 3. Dysthymia and Drug dependence

###  Lifetime estimates- UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-DRD", "DRD-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 50)
```


###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DYS-DRD", "DRD-DYS")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 50)
```

#   Table 3. Broadly-defined depression and substance use disorder
<br>
<br>
<br>
<br>

## 1. Depression and Alcohol abuse

###  Lifetime estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALA", "ALA-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Lifetime estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALA", "ALA-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

###  Period-prevalence estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALA", "ALA-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Period-prevalence estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALA", "ALA-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```

## 2. Depression and Alcohol dependence

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALD", "ALD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
``` 

###  Lifetime estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALD", "ALD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALD", "ALD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-ALD", "ALD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 30)
```

## 3. Depression and Alcohol use disorder

###  Lifetime estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-AUD", "AUD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
``` 

###  Lifetime estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-AUD", "AUD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

###  Period-prevalence estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-AUD", "AUD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Period-prevalence estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-AUD", "AUD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```

## 4. Depression and Drug abuse

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DRA", "DRA-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

##  Period-prevalence estimates - UNADJUSTED

```{r, echo = FALSE  }
a1<- c("DEP-DRA", "DRA-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

## 5. Depression and Drug dependence

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DRD", "DRD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```

###  Period-prevalence estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DRD", "DRD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 40)
```

###  Period-prevalence estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DRD", "DRD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

## 6. Depression and Drug use disorder

###  Lifetime estimates - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DUD", "DUD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
``` 

###  Lifetime estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DUD", "DUD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 40)
```

###  Period-prevalence estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DUD", "DUD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 20)
```

###  Period-prevalence estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("DEP-DUD", "DUD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

## 7. Depression and Cannabis dependence
###  Lifetime estimates - UNADJUSTED

```{r, echo = FALSE  }
a1<- c("DEP-MARD", "MARD-DEP")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 30)
```

## 8. Depression and Nicotine dependence
###  Period-prevalence estimates - ADJUSTED

```{r, echo = FALSE  }
a1<- c("DEP-NICD", "NICD-DEP")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

#   Table 4. Broadly-defined bipolar disorder and substance use disorder
<br>
<br>
<br>
<br>

## 1. Bipolar disorder and Alcohol abuse

###  Lifetime estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("BIPOLAR-ALA", "ALA-BIPOLAR")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

###  Period-prevalence estimates  - ADJUSTED
```{r, echo = FALSE  }
a1<- c("BIPOLAR-ALA", "ALA-BIPOLAR")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 20)
```

## 2. Bipolar disorder and Alcohol dependence

###  Lifetime estimates - ADJUSTED
```{r, echo = FALSE  }
a1<- c("BIPOLAR-ALD", "ALD-BIPOLAR")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

## 3. Bipolar disorder and Alcohol use disorder

###  Period-prevalence estimates - ADJUSTED

```{r, echo = FALSE  }
a1<- c("BIPOLAR-AUD", "AUD-BIPOLAR")
ma22<- ma2 %>% filter(pair %in% a1  & temporality_type == "PP") %>% 
   filter(adj_indicator == "1") %>%
  filter(adj_type == "overall")
adj_fn(-1, 10)
```

## 4. Bipolar disorder and Substance use disorder
###  Lifetime estimates  - UNADJUSTED
```{r, echo = FALSE  }
a1<- c("BIPOLAR-SUD", "SUD-BIPOLAR")
ma11<- ma1 %>% filter(pair %in% a1  & temporality_type == "LT") %>% 
  filter(unadj_indicator == "1") %>%
  filter(unadjusted_type == "overall")
unadj_fn(-1, 10)
```
